Local real space operators for translating Stokes Q/U to E/B maps on the sphere

### 2017-10-19 article/sections/kernel_discussion.tex
added a notebook which computes the oscillations seen in the spectra of eb maps evaluated from localized convolution kernels. Added a discussion to the draft on constructing convolution kernels with different radial profiles

We have observed that the radial functions derived by evaluating the multipole sums to different maximum multipoles are self similar. Specifically these functions follow an interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx [\frac{\ell_{\rm max}}{\ell'_{\rm max}}]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions. We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property. Lets say the function ${}_rf(\beta, \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta_0$.  The function ${}_rf(\beta', \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point $\beta'=\beta_0$ at a smaller value of $\beta$ owing to the fact that $\ell_{\rm max}/\ell'_{\rm max}$ is greater than unity. The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.

>>>>

We have observed that the radial functions derived by evaluating the multipole sums to different maximum multipoles are self similar. Specifically these functions follow an interesting telescoping and scaling property: $${}_rf(\beta,2,\ell_{\rm max}) \approx \Big[\frac{\ell_{\rm max}}{\ell'_{\rm max}}\Big]^2{}_rf(\beta'=\frac{\ell_{\rm max}}{\ell'_{\rm max}} \beta ,2,\ell'_{\rm max}) \,,$$ where ${}_rf$ denotes all the different radial functions. We can understand the shifting left of the radial kernels on increasing the maximum multipole using this property. Lets say the function ${}_rf(\beta, \ell'_{\rm max})$ transition to being monotonously below some fraction of the global maxima at an angular distance of $\beta_0$.  The function ${}_rf(\beta', \ell_{\rm max})$, given $\ell_{\rm max} > \ell'_{\rm max}$, reaches the same transition point $\beta'=\beta_0$ at a smaller value of $\beta$ owing to the fact that $\ell_{\rm max}/\ell'_{\rm max}$ is greater than unity. The amplitude scaling of the functions is irrelevant since the transition point is always described in terms of the fraction of the global maxima of the function.
